---
title: "Figures and Tables"
author: "Arthur M. Albuquerque"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document:
          toc: yes
          toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	fig.align = "center",
	message = FALSE,
	warning = FALSE
)
```

```{r}
# Ensures the package "groundhog" is installed
if (!require("groundhog")) install.packages("groundhog")

# Install/Load packages
pkgs = c("rio",
         "here",
         "dplyr",
         "multinma",
         "metafor",
         "ggdist",
         "posterior",
         "janitor",
         "gt",
         "ggplot2",
         "patchwork")

groundhog::groundhog.library(pkgs, "2022-03-14")

# Load models

load(here::here("output/fits/pooled_MACE_FE.RData"))
load(here::here("output/fits/pooled_safety_FE.RData"))
```


# Figure 2B

```{r}
# Create function to automate data wrangling for forest plot

wrangle_forest_fun = function(network_object,
                              outcome_name){
  
# Extract SUCRA values
sucra = 
  multinma::posterior_rank_probs(network_object, 
                                 lower_better = T,
                                 sucra = T) |> 
  data.frame() |> 
  dplyr::select(parameter, sucra) |> 
  dplyr::mutate(sucra = round(sucra, 2)) |> 
  dplyr::arrange(desc(sucra)) |> 
  dplyr::rename("name" = parameter)

# Extract all posterior draws from treatment effect comparisons with AAS
draws = multinma::relative_effects(network_object,
                                   summary = F)

# Data wrangle to facilitate manipulation of these draws
draws_pivot = 
  draws$sims |> 
  posterior::as_draws_df() |> 
  tidyr::pivot_longer(cols = dplyr::starts_with("d["))


# Generate 95% highest-density intervals (HDI) for each treatment effect
CIs = 
  draws_pivot |> 
  dplyr::group_by(name) |> 
  # median and 95% HDI
  ggdist::median_hdi(.width = 0.95) |> 
  dplyr::select(name:.upper) |> 
  dplyr::mutate(interval = paste0(round(exp(value),2),
                                  " [",
                                  round(exp(.lower), 2),
                                  ", ",
                                  round(exp(.upper), 2),
                                  "]")
  )

# Calculate posterior probabilities of interest
probs = 
  draws_pivot |> 
  dplyr::group_by(name) |> 
  dplyr::summarise(pr08 = mean(value < log(0.8)),
                   pr1_lower = mean(value < log(1)),
                   pr1_greater = mean(value > log(1)),
                   pr125 = mean(value > log(1/0.8)),
                   prrope = mean(value > log(0.8) & value < log(1/0.8))) |> 
  dplyr::ungroup() |> 
  dplyr::mutate(dplyr::across(pr08:prrope, ~round(100*.,1)))


# Put all info together and rename treatment effects
both = 
  dplyr::left_join(CIs, sucra) |>
  dplyr::left_join(probs) |>
  dplyr::mutate(
    name = dplyr::case_when(
      name == "d[AAS]" ~ "AAS",
      name == "d[5_Rivaroxaban]" ~ "Rivaroxaban 5mg",
      name == "d[75_Clopidogrel]" ~ "Clopidogrel 75mg",
      name == "d[AAS_2.5_Rivaroxaban]" ~ "AAS + Rivaroxaban 2.5mg",
      name == "d[AAS_10_Prasugrel]" ~ "AAS + Prasugrel 10mg",
      name == "d[AAS_75_Clopidogrel]" ~ "AAS + Clopidogrel 75mg",
      name == "d[Pooled_Ticagrelor]" ~ "Pooled Ticagrelor"),
    
    outcome = outcome_name
    )

return(both)
}

# Apply function for MACE and Bleeding outcomes and put all data in a single
# data frame
altogether = 
  wrangle_forest_fun(network_MACE_pooled_FE,
                   outcome_name = "MACE") |> 
  dplyr::bind_rows(
    wrangle_forest_fun(network_safety_pooled_FE,
                       outcome_name = "safety")
    ) |> 
  # Necessary to be able to order according to SUCRA
  dplyr::arrange(sucra, outcome)
  
# Function to create custom forest plot
forest_fun = function(){
  
   x = 
     base::with(altogether, # define data frame of interest
              metafor::forest(
                x = value,      # point estimate
                ci.lb = .lower, # lower credible interval bound
                ci.ub = .upper, # upper credible interval bound
                ylim = c(-2.5, 14.5), # forest plot height
                rows= c(-2:3, 5.5:10.5), # treatment effects order in the Y axis
                xlim = c(-2.5, 4), # forest plot width
                ilab = cbind(interval, pr08, pr1_lower,
                             pr1_greater, pr125, prrope), # info on the right side
                ilab.xpos = 1+c(0.6, 1.2, 1.5, 1.8, 2.1, 2.4), # position of these info
                slab = name, # label on the left side
                order = desc(outcome), # order
                at=log(c(.4, .6, 0.8, 1, 1.25, 2, 3)), # X axis ticks
                refline = log(c(0.8, 1, 1/0.8)), # vertical lines
                annotate = F, # Remove default 95% CrI estimates
                atransf = exp, # exponentiate X-axis labels (data in log scale)
                pch = 19, # point estimate as circle
                psize = 1.4, # Circle size
                efac=0, # Remove vertical lines at interval bars
                header="Compared with AAS",
                xlab = "Hazard Ratio (log scale)",
                cex = 1, # Text size
                cex.lab = 1) # X axis label font size
  ) 

# ROPE gray area
graphics::rect(xleft = log(0.8), xright = log(1/0.8),
               ybottom = x$ylim[1] - 1, ytop = x$ylim[2] - 2,
               border = NA, # no borders
               col = grDevices::adjustcolor("gray70", alpha.f = 0.4))

# Headers
text(x$xlim[1], x$ylim[2] - 3,
     "MACE",
     pos = 4, # left-align
     font=4, # bold
     cex = 1.3)

text(x$xlim[1], x$ylim[2] - 10.5,
     "Bleeding",
     pos = 4, # left-align
     font=4, # bold
     cex = 1.3)

text((3.55 + 2.05)/2,
     x$ylim[2], 
     "Posterior Probability, %",
     #font=2,
     cex = 1)

# Horizontal line
segments(x0 = 2.05, x1 = 3.55,
         y0 = x$ylim[2] - 0.5, y1 = x$ylim[2] - 0.5)

graphics::text(1+c(0.6, 1.2, 1.5, 1.8, 2.1, 2.4),
               x$ylim[2] - 1, cex = 1,
               c("HR [95% CrI]", "< 0.80", "< 1.00",
                 "> 1.00", "> 1.25", "ROPE"))
}

# Save as PDF

# pdf(file = here::here("output", "plots",
#                       'forest.pdf'),
#     height=6, width=12)
# 
# forest_fun()
# 
# dev.off()

```

```{r}
# Show previously saved forest plot
knitr::include_graphics(here::here("output", "plots",
                                   "forest.png"))

```

Treatment effects compared to AAS on MACE and Bleeding outcomes, ordered according
to underlying SUCRA values. HR below 1.0 favors the experimental treatment.
On the left, treatment names are depicted. In the middle,
forest plot shows each treatment effect median and 95% credible intervals. Gray
area corresponds to the ROPE (from 0.8 to 1.25 HR). On the right, exact effect
sizes along with posterior probabilities are shown.

Abbreviations: ROPE, region of practical equivalence; HR, hazard ratio.


# Figure 3

```{r}
p1 = 
  # Extract ranking probabilities for MACE
  multinma::posterior_rank_probs(network_MACE_pooled_FE, lower_better = T) |> 
  dplyr::as_tibble() |> 
  dplyr::mutate(Outcome = "MACE") |> 
  # Extract ranking probabilities for Bleeding
  dplyr::bind_rows(
    posterior_rank_probs(network_safety_pooled_FE, lower_better = T) |> 
  dplyr::as_tibble() |> 
  dplyr::mutate(Outcome = "Bleeding")
  ) |> 
  # Rename treatment effects and re-order
  dplyr::mutate(
    parameter = dplyr::case_when(
      parameter == "d[AAS]" ~ "AAS",
      parameter == "d[5_Rivaroxaban]" ~ "Rivaroxaban 5mg",
      parameter == "d[75_Clopidogrel]" ~ "Clopidogrel 75mg",
      parameter == "d[AAS_2.5_Rivaroxaban]" ~ "AAS + Rivaroxaban 2.5mg",
      parameter == "d[AAS_10_Prasugrel]" ~ "AAS + Prasugrel 10mg",
      parameter == "d[AAS_75_Clopidogrel]" ~ "AAS + Clopidogrel 75mg",
      parameter == "d[Pooled_Ticagrelor]" ~ "Pooled Ticagrelor"),
    
    parameter = factor(parameter, levels = c("AAS + Prasugrel 10mg",
                                     "Clopidogrel 75mg",
                                     "AAS + Rivaroxaban 2.5mg",
                                     "AAS + Clopidogrel 75mg",
                                     "Pooled Ticagrelor",
                                     "Rivaroxaban 5mg",
                                     "AAS")),
    Outcome = factor(Outcome, levels = c("MACE", "Bleeding"))
    ) |> 
  
  # pivot_longer code below extracted from 
  # https://github.com/dmphillippo/multinma/blob/HEAD/R/nma_summary-class.R
  
  tidyr::pivot_longer(cols = dplyr::starts_with("p_rank"),
                      names_to = "rank", values_to = "probability",
                      names_pattern = "^p_rank\\[([0-9]+)\\]$",
                      names_transform = list(rank = as.integer)) |> 
  dplyr::mutate(probability = 100*probability) |> 
  
  # Plot!
  ggplot() + 
  aes(x = rank, y = probability, group = Outcome, color = Outcome,
      linetype = Outcome) +
  geom_line(size = 0.9) +
  scale_color_manual(values = c("forestgreen", "#802521")) +
  scale_x_continuous(breaks = seq(1, 7, 1)) +
  scale_y_continuous(breaks = seq(0, 100, 50),
                     limits = c(0, 110)) +
  labs(x = "Rank", y = "Probability (%)\n") +
  facet_wrap(~parameter, nrow = 3) +
  multinma::theme_multinma()

```

```{r}
mace_sucra = 
  # Extract SUCRA for MACE
  multinma::posterior_rank_probs(network_MACE_pooled_FE, 
                               lower_better = T,
                               sucra = T) |> 
  data.frame() |> 
  dplyr::select(parameter, sucra) |> 
  dplyr::mutate(sucra = round(sucra, 2)) |> 
  dplyr::arrange(desc(sucra)) |> 
  dplyr::mutate(outcome = "MACE")

safety_sucra = 
  # Extract SUCRA for Bleeding
  multinma::posterior_rank_probs(network_safety_pooled_FE, 
                               lower_better = T,
                               sucra = T) |> 
  data.frame() |> 
  dplyr::select(parameter, sucra) |> 
  dplyr::mutate(sucra = round(sucra, 2)) |> 
  dplyr::arrange(desc(sucra)) |> 
  dplyr::mutate(outcome = "Bleeding")

p2 = 
  # put both data frames together
  dplyr::bind_rows(mace_sucra, safety_sucra) |> 
  
  # Rename treatment effects and re-order
  dplyr::mutate(
    parameter = dplyr::case_when(
      parameter == "d[AAS]" ~ "AAS",
      parameter == "d[5_Rivaroxaban]" ~ "Rivaroxaban 5mg",
      parameter == "d[75_Clopidogrel]" ~ "Clopidogrel 75mg",
      parameter == "d[AAS_2.5_Rivaroxaban]" ~ "AAS + Rivaroxaban 2.5mg",
      parameter == "d[AAS_10_Prasugrel]" ~ "AAS + Prasugrel 10mg",
      parameter == "d[AAS_75_Clopidogrel]" ~ "AAS + Clopidogrel 75mg",
      parameter == "d[Pooled_Ticagrelor]" ~ "Pooled Ticagrelor"),
    parameter = factor(parameter, levels = rev(c("AAS + Prasugrel 10mg",
                                     "Clopidogrel 75mg",
                                     "AAS + Rivaroxaban 2.5mg",
                                     "AAS + Clopidogrel 75mg",
                                     "Pooled Ticagrelor",
                                     "Rivaroxaban 5mg",
                                     "AAS"))),
    outcome = factor(outcome, levels = c("MACE", "Bleeding"))
    ) |> 
  
  # Plot!
  ggplot() +
  aes(y = parameter, x = outcome, fill = sucra, label = sucra) +
  geom_tile() +
  geom_text(size = 4,
            aes(color = sucra > 0.6),
            show.legend = F) +
  scale_color_manual(values = c("black", "white")) +
  scale_fill_gradientn("SUCRA",
                       breaks=c(0, 0.50, 1),
                       limits = c(-0.1, 1.1),
                       colors = MetBrewer::met.brewer("OKeeffe2")) +
  scale_x_discrete(expand = c(0,0)) +
  scale_y_discrete(expand = c(0,0)) +
  labs(x = NULL, y = NULL) +
  theme(axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank())
```

```{r, fig.width = 11}
# Show both plots together
p1 + p2 + patchwork::plot_annotation(tag_levels = "A") +
  patchwork::plot_layout(widths = c(5, 1))
```

Panel A: Ranking probabilities for MACE (solid line) and Bleeding (dotted line)
outcomes for each treatment.
Panel B: Heatmap with corresponding SUCRA values. While each row corresponds to
a treatment, each column depicts one outcome. 


